Computer Science House Constitution

### 2022-02-16 constitution.tex
waivers: move towards 3/4 vote

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\asubsection{Operations of the Evaluations Directorship}
\asubsubsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\asubsubsubsection{The Evaluation Period}
The Process will occur either once or twice per semester, and will last for six (6) weeks.
The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
\asubsubsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active Members who have passed a Membership Evaluation, all Active Resident Members, all Introductory Resident Members, and ten (10) of any combination of the following:
\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
\asubsubsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

@@

@@

\asection{Number of Votes Required}
The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass.
Below are listed four standard votes.
Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority}
In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
\asubsection{Fifty Percent}
In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-Thirds}
In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three Tiered}
When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest or highest option will only pass if the votes cast for that selection exceed fifty percent of the Total Number of Votes Cast.
If neither the highest or lowest selection exceeds fifty percent, the middle option will then automatically be passed.
In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.

>>>>

% BY-LAW IV - OPERATIONS OF THE EVALUATIONS DIRECTORSHIP
\asubsection{Operations of the Evaluations Directorship}
\asubsubsection{The Introductory Process}
The Introductory Process is designed to provide an easy means for Introductory Members to meet existing House members, learn House history, demonstrate their involvement potential to House, and allow existing House members to evaluate them for Active Membership.
\asubsubsubsection{The Evaluation Period}
The Process will occur either once or twice per semester, and will last for six (6) weeks.
The Process shall be initiated by the Evaluations Director during either the first and second week of each semester.
The Executive Board may hold a closed ballot Simple Majority vote to extend the Introductory Process or the Introductory Packet.
If an Introductory Process is extended, the Introductory Evaluation shall occur at the termination of the extended Process, which may be outside of the period defined in \ref{Introductory Evaluation}.
If deemed necessary by the Evaluations Director, or by an Executive Board simple majority vote, the second intro process must begin within nine (9) days of the first process ending.
If a second Introductory Process is approved, the Evaluations Director may initiate a new Introductory Packet within the first or second week of the Introductory Process.
\asubsubsubsection{The Introductory Packet}
Each Introductory Process participant, after the first week, is given two (2) weeks to return a document that should contain a signature from all Active members, all Introductory Resident members, and ten (10) of any combination of the following:
\begin{itemize}
	\item Alumni members
	\item Honorary members
	\item Advisory members
\end{itemize}
At the discretion of the Evaluations Director, any Introductory Packet may be extended to accommodate extenuating circumstances.
\asubsubsubsection{Expectations of an Introductory Member}
Before the end of the Process, an Introductory Member is expected to:
\begin{itemize}
\item Attend all House meetings during the process
\item Complete the Introductory Packet
\item Attend at least one House directorship meeting for each week of the process (including permanent and Ad Hoc directorship meetings)
\item Attend at least one House social event during the process
\item Attend at least two seminars relating to computing or electronics
\item Sign a copy of the Membership Agreement describing a House Member’s responsibilities and expectations
\end{itemize}

@@

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item House may choose to waive the following subset of the Qualifications for Executive Board positions (defined under \ref{Qualifications}) for all Candidates:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item When a waiver is proposed, the Chair of the Vote shall state which Executive Board position and Qualification is being voted upon, and any nominated Candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
  \item A Three-Quarters Immediate Vote, as defined in \ref{Three-Quarters} and \ref{Immediate Vote}, is then taken to determine whether the proposed waiver shall take effect.
  \item Each vote to waive a Qualification must only apply to a single Qualification for a single Executive Board position.
  \item Waivers always apply to all Candidates for the Executive Board position.
\end{enumerate}

@@

\asection{Number of Votes Required}
The Number of Votes Required refers to the numbers required to achieve a quorum and for a vote to pass.
Below are listed four standard votes.
Numbers for non-standard votes are defined in the section describing the actual vote.
\asubsection{Simple Majority}
In a Simple Majority Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option is larger than the number of votes cast for every other option individually.
\asubsection{Fifty Percent}
In a Fifty Percent Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds one-half the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for that option exceeds fifty percent of the Total Number of Votes Cast.
\asubsection{Two-Thirds}
In a Two-thirds Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds two-thirds of the Total Number of Votes Cast.
\asubsection{Three-Quarters}
In a three-quarters Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds three-quarters the Total Number of Possible Votes.
An option in the vote passes if the number of votes cast for the option equals or exceeds three-quarters of the Total Number of Votes Cast.
\asubsection{Three Tiered}
When voting on a set of three choices where each choice can be ranked in a definite order, a selection for either the lowest or highest option will only pass if the votes cast for that selection exceed fifty percent of the Total Number of Votes Cast.
If neither the highest or lowest selection exceeds fifty percent, the middle option will then automatically be passed.
In a Three-Tiered Vote, a Quorum is reached if the Total Number of Votes Cast is equal to or exceeds two-thirds of the Total Number of Possible Votes.
